Transcriptomics Analysis of Expressions of Ten genes and Their Prognostic Value in Head and Neck Squamous Cell Carcinoma

### 2021-06-18 Cover_letter_JPM.tex
Answer 2-1 done

% 1) 本來就有計算 FDR and excluding >= 0.05 (ok)
% 2) and FDR (done)
We appreciate the reviewer to kindly advise us about the principle of sliding window cutoff selection in detail.
% and give us this nomenclature as "sliding window"
%% *** 準備一張 3/20 candidates: accumulated \textit{P}-value plots 來說明，其實這些 P values 不論 50% cut or 70% 幾乎都 far less than 0.05, even < 0.001
We have corrected our statement of this workflow (please see Answer 2-2).
We provide more evidence to validate them (please see Answer 2-3).

We understand that the sliding-window selection of cutoffs would capture more genes whose \textit{P} values just reach the significant level (\textit{P}=0.05).
%http://bioinformatica.mty.itesm.mx:8080/Biomatec/SurvivaX.jsp run TCGA2016 in median (median cutoff; not case number 50\% 50\%)
%=> defense: 
%% *** 準備一張 20 candidates: accumulated \textit{P}-value plots 來(like Figure 4: (Please see supplementary Figure SXXX))
%說明，其實這些 P values 不論 50% cut or 70% 幾乎都 far less than 0.05
% file: 1453 Feb 15 2020 ./intermediate_data/HNSCC_OS_marginSFP_pvalueBonferroni_KM_candidate_cox.Rda => candidate_sample
%[1] "HNSCC_OS_marginS_pvalueBonferroni_sorted"   
%[2] "HNSCC_OS_marginFree_pvalueBonferroni_sorted"
%[3] "HNSCC_OS_marginPlus_pvalueBonferroni_sorted"
According to our results, the preliminary biomarkers have FDR-corrected \textit{P} values from \num{1e-4} to 0.04 whatever grouped by cutoffs at 50\% quantile cutoff or at 70\% quantile cutoff (Please see Figure \ref{fig:figure4} in this cover letter; it is also shown in manuscript as updated "Figure 4").

Moreover, in the special case, one of our 20 preliminary candidates, gene "NDFIP1", 
%Rplot_pvaluePlot_NDFIP1.pdf
%  to find cases_OS outside of range 180-220 (== cutoff not at median)
%# pvalue plot as 倒V字形 "^" or W p_OS pvalues plots (with local minials)
% # 99 genes have one p_OS >= 0.05, in OS_pvalueTex005
%# 3641 genes have one p_OS >= 0.02, in OS_pvalueTex002
%# special case: HNSCC_survivalAnalysis_marginS_NDFIP1.xlsx
%# NDFIP1 (within our 20 preliminary candidates), 
will be kick-out prematurely in "median cutoff" of survival analysis.
In the \textit{P} value plot (Figure \ref{fig:pvaluePlot_NDFIP1}, and also in 
supplementary figure ??), we could see a sliding-window selection with cutoff finding might collect more candidate (\textit{P} $<0.05$) for further Cox's modeling.
Indeed, it needs to be validated by the other independent cohort.
%as Rplot_pvaluePlot_NDFIP1.pdf

% supplementary figure
\begin{figure}
    \centering
    \includegraphics[width=10cm]{Rplot_pvaluePlot_NDFIP1.pdf}
    \caption{Under cutoff-finding procedure of Kaplan-Meier analysis, the \textit{P}-value plot of gene "NDFIP1" shows: 1) 70\% of \textit{P} value is $<0.05$; 2) the middle part (zoom-in and revealed in inset box) has a "W" curve; 3) sliding-window cutoff selection could find it's optimized \textit{P} values while a median cut might yield \textit{P} value $<0.05$ or $>0.05$ by chance.}
    \label{fig:pvaluePlot_NDFIP1}
\end{figure}

@@

>>>>

% 1) 本來就有計算 FDR and excluding >= 0.05 (ok)
% 2) and FDR (done)
We appreciate the reviewer to kindly advise us about statistical consideration of sliding window cutoff selection in detail.
% and give us this nomenclature as "sliding window"
%% *** 準備一張 3/20 candidates: accumulated \textit{P}-value plots 來說明，其實這些 P values 不論 50% cut or 70% 幾乎都 far less than 0.05, even < 0.001
We have corrected our statement of this workflow (please see Answer 2-2).
We also provide more evidence to validate them by an independent HNSCC cohort (GSE65858) (please see Answer 2-3).

We understand that the sliding-window selection of cutoffs would capture more genes whose \textit{P} values just reach the significant level (\textit{P}=0.05).
%http://bioinformatica.mty.itesm.mx:8080/Biomatec/SurvivaX.jsp run TCGA2016 in median (median cutoff; not case number 50\% 50\%)
%=> defense: 
%% *** 準備一張 20 candidates: accumulated \textit{P}-value plots 來(like Figure 4: (Please see supplementary Figure SXXX))
%說明，其實這些 P values 不論 50% cut or 70% 幾乎都 far less than 0.05
% file: 1453 Feb 15 2020 ./intermediate_data/HNSCC_OS_marginSFP_pvalueBonferroni_KM_candidate_cox.Rda => candidate_sample
%[1] "HNSCC_OS_marginS_pvalueBonferroni_sorted"   
%[2] "HNSCC_OS_marginFree_pvalueBonferroni_sorted"
%[3] "HNSCC_OS_marginPlus_pvalueBonferroni_sorted"
According to our results, the preliminary biomarkers have FDR-corrected \textit{P} values from \num{1e-4} to 0.04 which have been grouped by cutoffs at 50\% or at 70\% quantile cutoff (Please see Figure \ref{fig:figure4}; it is also shown in manuscript as updated "Figure 4").
Moreover, the gene NDFIP1, one of our 20 preliminary candidates, has a \textit{P} value (around $0.05$) at 50\% quantile cutoff, achieving a p-value of \num{1e-6} at 70\% quantile cutoff. After the FDR correction, NDFIP1 still has \textit{P} value of \num[3]{0.0001074233}.
%Rplot_pvaluePlot_NDFIP1.pdf
%  to find cases_OS outside of range 180-220 (== cutoff not at median)
%# pvalue plot as 倒V字形 "^" or W p_OS pvalues plots (with local minials)
% # 99 genes have one p_OS >= 0.05, in OS_pvalueTex005
%# 3641 genes have one p_OS >= 0.02, in OS_pvalueTex002
%# special case: HNSCC_survivalAnalysis_marginS_NDFIP1.xlsx
%# NDFIP1 (within our 20 preliminary candidates), 
In the \textit{P} value plot (Figure \ref{fig:pvaluePlot_NDFIP1}, and also in 
supplementary figure ??), we could see a sliding-window selection with cutoff finding might collect more candidate (\textit{P} $<0.05$) for further Cox's modeling.
%Some useful biomarkers might be kick-out prematurely in "median cutoff" of survival analysis.
Indeed, it needs to be validated by the other independent cohort.

@@

%as Rplot_pvaluePlot_NDFIP1.pdf
%Moreover, in the special case, one of our 20 preliminary candidates, gene "NDFIP1",

% supplementary figure
\begin{figure}[ht]
    \centering
    \includegraphics[width=10cm]{Rplot_pvaluePlot_NDFIP1.pdf}
    \caption{Under cutoff-finding procedure of Kaplan-Meier analysis, the \textit{P}-value plot of gene "NDFIP1" shows: 1) 70\% of \textit{P} value is $<0.05$; 2) the median-cut zone (zoom-in and revealed in inset box) has a "W"-like distribution; 3) sliding-window cutoff selection could find it's optimized \textit{P} values (far less than 0.001) while a median cut might yield \textit{P} value $>=0.05$.\\
    (x-axis: grouping by person number; y-axis: \textit{P} value in log10 transformed)}
    \label{fig:pvaluePlot_NDFIP1}
\end{figure}
